
The goal of this section is to derive an integral equation for the pair-distribution function called the Kirkwood equation.
For this, one can use a system with two kinds of particles,
just as the system that was used to express the chemical potential using the pair-distribution function. ADD EQ. REF
In this system the interaction potential of particle 1 with any of the other particles is scaled by $\xi$:
\begin{align}\label{eq:kirkwood:UN_xi}
U_N(\rr_1,..,\rr_N) = \sum_{j=2}^{N} \xi u(\rr_1,\rr_j)
+ \sum_{\substack{i=2 \\ j>i}}^N u(\rr_i,\rr_j),
\end{align}
with $0 \leq \xi \leq 1$,
so when $\xi = 1$ it is a system of $N$ identical interacting particles,
and when $\xi = 0$ it is a system consisting of one ideal particle and $N-1$ interacting particles.
Because there are two species of particles in this system (particle 1 and the 
"normal" particles),
this means that one can define two kinds of radial distribution functions:
one for the distribution of the normal particles around particle 1,
one for the distribution of the normale particles around an other normal particle.
In these notes, the difference between these two functions is indicated by the arguments.
When $\rr_1$ is one of the arguments (or $|\rr_1 - \rr_j|$ with $j>2$),
it is the first kind; otherwise it is the second kind.
When which distribution function is which is not clear from the arguments,
I indicate the distribution function of the normal particles around particle 1 with
$g^{(n)}_{(1,n)}(...)$ and the other kind with $g^{(n)}_{(n,n)}(...)$.

The starting point is the identity
\begin{align}
kT~ln\left(\rho^{(n)}(\rr_1,..,\rr_n;\xi)\right) =
&~ kT~ln\left(\rho^{(n)}(\rr_1,..,\rr_n;\xi=0)\right) + \nonumber \\
& \int_0^\xi d\xi' \frac{\partial}{\partial \xi'}
kT~ln\left(\rho^{(n)}(\rr_1,..,\rr_n;\xi')\right).
\end{align}
All that is to be done is to work out what the derivative on the right hand side is.
For simplicity, I will do the $n=2$ case here, and show the general case in App. \ref{sec:app_kirkwood}.
We need the derivative with respect of $\xi$ of
\begin{align}
\rho^{(2)}(\rr_1,\rr_2;\xi) =
\frac{N(N-1)}{Z_N(\xi)} \int d\rr_3 \cdots \int d\rr_N~
e^{-\beta U_N(\xi)}.
\end{align}
This is
\begin{align}\label{eq:kirkwood:first_deriv}
k T \frac{\rho^{(2)}(\partial \rr_1,\rr_2;\xi)}{\partial \xi} &=
\frac{N(N-1)}{Z_N(\xi)} \int d\rr_3 \cdots \int d\rr_N~
    e^{-\beta U_N(\xi)}. \\
&= 
    \underbrace{kT N (N-1) \left( \frac{\partial}{\partial \xi}
    \frac{1}{Z_N(\xi)} \right)
    \int d\rr_3 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)}
    }_{ \equiv I_1}
    \nonumber \\
    &~~~~~~
    +\underbrace{ kT \frac{N(N-1)}{Z_N(\xi)}
    \int d\rr_3 \cdots \int d\rr_N~
    \frac{\partial}{\partial \xi}e^{-\beta U_N(\xi)}
    }_{\equiv I_2}.
\end{align}
The first integral is
\begin{align}
I_1 &= -\frac{kT N(N-1)}{Z_n(\xi)^2}
    \left( \frac{\partial}{\partial \xi}
        \underbrace{
        \int d\rr_1 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)}
        }_{Z_N(\xi)}
    \right)
    \int d\rr_3 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)} \\
&= \rho^{(2)}(\rr_1,\rr_2;\xi) \frac{-kT}{Z_N(\xi)}
    \int d\rr_1 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)}
        \frac{\partial}{\partial \xi}
        \left( - \beta U_N(\xi) \right).
\end{align}
The $-\beta$ cancels the $-kT$ in the fraction, and the derivative in the integral is $\partial_\xi U_N = \sum_{j=2}^N u(\rr_1,\rr_j)$ (see \eqref{eq:kirkwood:UN_xi}).
There are $N-1$ terms in this sum.
Each term has the same contribution because the $\rr$'s are all integration parameters.
Therefore, one can pick one of the terms in the sum, say $u(\rr_1,\rr_2)$, and multiply the result by $N-1$.
This results in
\begin{align}
I_1 &= \rho^{(2)}(\rr_1,\rr_2;\xi)\frac{1}{N}
    \int d\rr_1 \int d\rr_2 u(\rr_1,\rr_2)
    \frac{N(N-1)}{Z_N(\xi)}
    \int d\rr_3 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)},
\end{align}
where I multiplied and divided by N because the second fraction and the second set of integrals is $\rho^{(2)}(\rr_1,\rr_2;\xi)$.
So the integral is
\begin{align}
I_1 &= \rho^{(2)}(\rr_1,\rr_2;\xi)\frac{1}{N}
    \int d\rr_1 \int d\rr_2 u(\rr_1,\rr_2)
    \rho^{(2)}(\rr_1,\rr_2;\xi).
\end{align}

For the second integral in Eq. \eqref{eq:kirkwood:first_deriv} we need
\begin{align}
kT \frac{\partial}{\partial \xi} 
    e^{-\beta U_N(\xi)} 
&= - e^{-\beta U_N(\xi)} \frac{\partial}{\partial \xi}
    U_N \\
&= - e^{-\beta U_N(\xi)} \sum_{j=2}^N u(\rr_1,\rr_j) \\
&=- e^{-\beta U_N(\xi)}\left(
    u(\rr_1,\rr_2) +  \sum_{j=3}^N u(\rr_1,\rr_j)
    \right).
\end{align}
The sum in the last line has $N-2$ terms, so one can
replace the sum by a single term,say $u(\rr_1,\rr_3)$, and multiply by the number of terms.
This gives
\begin{align}
I_2 &= -u(\rr_1,\rr_2) \frac{N(N-1)}{Z_N(\xi)}
    \int d\rr_3 \cdots \int d\rr_N~ e^{-\beta U_N(\xi)}\\
    &~~~~~- \frac{N(N-1)(N-2)}{Z_N(\xi)}
        \int d\rr_3 u(\rr_1,\rr_3) \int d\rr_4 \cdots
        \int d\rr_N~ e^{-\beta U_N(\xi)} \\
&= -u(\rr_1,\rr_2)\rho^{(2)}(\rr_1,\rr_2;\xi) 
    - \int d\rr_3 u(\rr_1,\rr_3) \rho^{(3)}(\rr_1,\rr_2,\rr_3;\xi).
\end{align}
